\nonstopmode{}
\documentclass[a4paper]{book}
\usepackage[times,inconsolata,hyper]{Rd}
\usepackage{makeidx}
\usepackage[utf8,latin1]{inputenc}
% \usepackage{graphicx} % @USE GRAPHICX@
\makeindex{}
\begin{document}
\chapter*{}
\begin{center}
{\textbf{\huge Package `modelwordcloud'}}
\par\bigskip{\large \today}
\end{center}
\begin{description}
\raggedright{}
\item[Title]\AsIs{Model Word Clouds}
\item[Version]\AsIs{0.1}
\item[Author]\AsIs{Peter Hurford }\email{peter@peterhuford.com}\AsIs{ [aut, cre]}
\item[Maintainer]\AsIs{Peter Hurford }\email{peter@peterhuford.com}\AsIs{}
\item[Description]\AsIs{Make a word cloud out of text associated with a model.}
\item[License]\AsIs{LGPL-2.1}
\item[LazyData]\AsIs{true}
\item[Imports]\AsIs{methods, graphics, stats}
\item[RoxygenNote]\AsIs{6.0.1}
\end{description}
\Rdcontents{\R{} topics documented:}
\inputencoding{utf8}
\HeaderA{wordcloud}{Make a word cloud.}{wordcloud}
%
\begin{Description}\relax
Make a word cloud.
\end{Description}
%
\begin{Usage}
\begin{verbatim}
wordcloud(words, freq, coefficients = NULL, colors = "black", scale = c(4,
  0.5), min_freq = 3, max_words = Inf, random_order = FALSE,
  random_color = FALSE, rot_per = 0, bg_color = "#FFFFFF")
\end{verbatim}
\end{Usage}
%
\begin{Arguments}
\begin{ldescription}
\item[\code{words}] character. A vector of words to plot.

\item[\code{freq}] numeric. The frequency of those words.

\item[\code{coefficients}] numeric. If provided, colors will be assigned according to coefficients.

\item[\code{colors}] character. The colors to use for plotting.

\item[\code{scale}] numeric. The range of sizes.

\item[\code{min\_freq}] numeric. Words with less frequency than this will not be plotted.

\item[\code{max\_words}] numeric. Don't plot more words than this amount.

\item[\code{random\_order}] logical. Should words be plotted in a random\_order or by frequency (default FALSE)?

\item[\code{random\_color}] logical. Allocate words a color by random? (default FALSE).

\item[\code{rot\_per}] numeric. Amount of rotation to apply to each word, between 0 and 1. Defaults to 0 (no rotation).

\item[\code{bg\_color}] character. The color of the background.
\end{ldescription}
\end{Arguments}
\printindex{}
\end{document}
